### 2011-04-11 Spatial_adaptation/standing-variation.tex
/* Standing variation */ mathematica solves a cubic
/* Standing variation */ mathematica does integrals

@@

>>>>

\subsection{Mathematica says}

...that 
\begin{align}
    \int_0^\infty \exp\left( - \lambda \pi v^2 (t^2/s_d + t^3) \right) dt 
       = \frac{ 1 }{ 27 s_d } \left(
            \exp\left( - \frac{2 \pi v^2 \lambda}{27 s_d^3} \right) 2 \sqrt{3} \pi 
                \left( I_{-1/3}\left( \frac{2 \pi v^2 \lambda}{27 s_d^3} \right) 
                    + I_{1/3}\left( \frac{2 \pi v^2 \lambda}{27 s_d^3} \right) 
            \right)
            - {}_2F_2\left(\frac{1}{2},1;\frac{2}{3},\frac{4}{3};-\frac{4 \pi v^2 \lambda}{27 s_d^3}\right)
        \right) ,
\end{align}
where $I_n(x)$ is the modified Bessel function of the first kind (solves $z^2 y''(z) + z y'(z) - (z^2 + n^2) y = 0$),
and ${}_2F_2(\cdot)$ is the generalized hypergeometric function.

...and
\begin{align}
    \int_0^\infty \frac{2\lambda \pi v}{s_d} t \exp\left( - \lambda \pi v^2 (t^2/s_d + t^3) \right) dt \right) dt 
        = \frac{1}{v s_d} - \frac{1}{2 s_d^2} \exp{ \frac{\pi v^2 \lambda}{4 s_d^2} \pi \sqrt{\lambda} \left( 1 - \Phi\left( \frac{ v \sqrt{\pi v} }{ 2 s_d } \right) \right) .
\end{align}

@@

\subsection{Mathematica Says}

... (and Wikipedia too) that the solutions to $ax^2 + bx^3 = 1$ are:
let 
\[
   u = \left( -2a^3 + 27b^2 + 3 \sqrt{3} \sqrt{ -4a^3b^2+27b^4} \right)
\]
and $(1, r, \bar r)$ are the cube roots of $1$, with $r=(1+i\sqrt{3})/2$ then
\[
    x = \begin{cases} 
        -\frac{a}{3b} + \frac{ 2^{1/3} a^2 }{ 3 b u^{1/3} } + \frac{ u^{1/3} }{ 3 b 2^{1/3} } \\
        -\frac{a}{3b} + r \frac{ 2^{1/3} a^2 }{ 3 b u^{1/3} } + \bar r \frac{ u^{1/3} }{ 3 b 2^{1/3} } \\
        -\frac{a}{3b} + \bar r \frac{ 2^{1/3} a^2 }{ 3 b u^{1/3} } + r \frac{ u^{1/3} }{ 3 b 2^{1/3} }  .
    \end{cases}
\]
Plugging in $a=\pi \lambda_0$ and $b=\pi \lambda v$ we get
$u = - 2 \pi^3 \lambda_0^3 + 3 \pi^2 \left( 9 v^2 \lambda^2 + \sqrt{ 81 b^4 \lambda^4 - 12 \pi v^2 \lambda^2 \lambda_0^3 } \right)$
... and the whole expression is ugly.
